%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {B2B Order - Development Captain} % Job title
    {Fashion Cloud B.V.} % Organization
    {Amsterdam, Netherlands} % Location
    {Jul. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Regularly collaborate with product managers and designers to create solutions for the platform}
        \item {Plan implementation of solutions, create digestible tickets and handle their delegation}
        \item {Handle cross team communication to ensure no one is blocked}
        \item {Proactively identify problems in the platform and create RFCs to address them}
        \item {Give regular feedback and appraisals}
        \item {Provide support to my colleagues in their tasks}
        \item {Stack: Angular, TypeScript, LESS, Node (Express), MongoDB, AWS (S3, EventBridge)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Unstack (Shopify Landing Page Platform) - Senior Frontend Developer} % Job title
    {Arbisoft} % Organization
    {Lahore, Pakistan} % Location
    {Jan. 2022 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assist with implementation of custom flavor of JSX for purposes of template creation.}
        \item {Improve UX by adding additional properties and improving styles for template building blocks.}
        \item {Stack: React, Redux, TypeScript, SCSS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hirestream (In-House ATS Solution) - Full Stack Developer} % Job title
    {} % Organization
    {} % Location
    {Mar. 2019 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setup JWT authorization.}
        \item {Implement custom rich text editor.}
        \item {Automate request feedback using Redux and custom middleware.}
        \item {Implement OAuth to connect with LinkedIn, Twitter and Google.}
        \item {Add Web Socket support for continuous user feedback.}
        \item {Implement payments using Stripe.}
        \item {Contribute most of the pages for the frontend using React.}
        \item {Stack: React, Redux, TypeScript, SCSS, Django, PostgreSQL}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Workstream (In-House ERP Solution) - Full Stack Developer} % Job title
    {} % Organization
    {} % Location
    {Dec. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactor codebase by shifting React class components to functional components.}
        \item {Create new pages using React and Redux.}
        \item {Improve test coverage using Django tests and JEST.}
        \item {Stack: React, Redux, TypeScript, SCSS, Django, PostgreSQL}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented complex data crawlers using Scrapy, Splash and Js2Py.}
        \item {Create a demo app to showcase benefits of Golang for data crawling.}
        \item {Implement automation suite using Selenium.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
