%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Open Source Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------


\cventry
{Rich text editor for Material UI} % Description
{Material RTE} % Name
{\href{https://www.npmjs.com/package/material-rte}{\color{awesome-skyblue}NPM LINK} - \href{https://github.com/Ali60351/material-rte}{\color{awesome-skyblue}GITHUB LINK}} % LINK
{} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Implement a Rich Text Editor using Draft JS as a base.}
\item {Style it using Material UI theme and add support for custom theme.}
\item {Add additional features like variable support and hyperlinks.}
\item {Made with React JS and TypeScript.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Find Voice Actor Links in your Anime History} % Description
{Seiyuu Nostalgia} % Name
{\href{https://github.com/Ali60351/seiyuu-nostalgia}{\color{awesome-skyblue}GITHUB LINK} - \href{https://ali60351.github.io/seiyuu-nostalgia/}{\color{awesome-skyblue}WEBSITE LINK}} % LINK
{} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Dive into all watched shows and shows all roles acted by a certain voice actor.}
\item {Made with Vue JS and GraphQL.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{API to easily convert and resize images} % Description
{Image Processing API} % Name
{\href{https://github.com/Ali60351/image-processing-api}{\color{awesome-skyblue}GITHUB LINK}} % LINK
{} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Implement image resizing and conversion using Sharp.}
\item {API implemented with ExpressJS and TypeScript.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A tool to quickly verify file integrity} % Description
{Quick-FIV} % Name
{\href{https://github.com/Ali60351/Quick-FIV}{\color{awesome-skyblue}GITHUB LINK} - \href{https://github.com/Ali60351/Quick-FIV/wiki}{\color{awesome-skyblue}WIKI LINK}} % LINK
{} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Developed application to verify integrity of files in inside a folder recursively.}
\item {Functions by storing hashes of all files present inside a folder inside a JSON file.}
\item {Made with NodeJS, Electron, Vue JS and Vuetify JS.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{An application to stay up to date with in game information directly through your desktop} % Description
{Warframe Alerts} % Name
{\href{https://github.com/WFCD/warframe-alerts-win}{\color{awesome-skyblue}GITHUB LINK}} % LINK
{} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Utilizes official RSS feed as data source.}
\item {Created with C-Sharp and Windows Forms API.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}